---
title: 'Testing Simulation: Monopoly'
output:
  pdf_document: default
  html_document: default
date: "2022-11-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = "hide"
  )
rm(list = ls())
library(Dispatching)
library(foreach)
library(magrittr)
library(codetools)
library(ggplot2)
library(kableExtra)
```

# Set constant

```{r}
seed <- 1
set.seed(seed)
n_ths <- 2
t <- 1
multistart <- 10
solver <- "nleqslv"
```

# Generate the baseline equilibrium

```{r}
equilibrium <-
  generate_equilibrium(
    n_ths = n_ths,
    seed = seed
  )
```

# Comparative statics {.tabset}

## Setting

```{r, results = "asis"}
equilibrium
```

## Check the foc at the baseline

```{r, results = "asis"}

equilibrium <-
    solve_equilibrium_profit_t(
      t = t,
      equilibrium = equilibrium
    )


g <-
  seq(
    -10,
    6,
    by = 0.1
  ) %>%
  purrr::map(
    function(x) {
      w_x <- equilibrium$endogenous[[t]]$w
      w_x[2] <- x
      foc <-
        compute_foc_t(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          gamma_w = equilibrium$parameter$gamma_w,
          gamma_f = equilibrium$parameter$gamma_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a = equilibrium$exogenous[[t]]$x_a,
          x_c = equilibrium$exogenous[[t]]$x_c,
          size_w = equilibrium$exogenous[[t]]$size_w,
          size_f = equilibrium$exogenous[[t]]$size_f,
          owner = equilibrium$exogenous[[t]]$owner,
          mu = equilibrium$shock[[t]]$mu,
          ea_w = equilibrium$shock[[t]]$ea_w,
          ea_f = equilibrium$shock[[t]]$ea_f,
          ec_w = equilibrium$shock[[t]]$ec_w,
          ec_f = equilibrium$shock[[t]]$ec_f,
          w = w_x,
          f = equilibrium$endogenous[[t]]$f,
          s_f = equilibrium$endogenous[[t]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      return(
        tibble::tibble(
          x = x,
          foc_1 = foc[2]
        )
      )
    }
  ) %>%
  dplyr::bind_rows()

g %>%
  ggplot(
    aes(
      x = x,
      y = foc_1
    )
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  theme_classic()
```

```{r, results = "asis"}
g <-
  seq(
    0.1,
    15,
    by = 0.1
  ) %>%
  purrr::map(
    function(x) {
      f_x <- equilibrium$endogenous[[t]]$f
      f_x[2] <- x
      foc <-
        compute_foc_t(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          gamma_w = equilibrium$parameter$gamma_w,
          gamma_f = equilibrium$parameter$gamma_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a = equilibrium$exogenous[[t]]$x_a,
          x_c = equilibrium$exogenous[[t]]$x_c,
          size_w = equilibrium$exogenous[[t]]$size_w,
          size_f = equilibrium$exogenous[[t]]$size_f,
          owner = equilibrium$exogenous[[t]]$owner,
          mu = equilibrium$shock[[t]]$mu,
          ea_w = equilibrium$shock[[t]]$ea_w,
          ea_f = equilibrium$shock[[t]]$ea_f,
          ec_w = equilibrium$shock[[t]]$ec_w,
          ec_f = equilibrium$shock[[t]]$ec_f,
          w = equilibrium$endogenous[[t]]$w,
          f = f_x,
          s_f = equilibrium$endogenous[[t]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      return(
        tibble::tibble(
          x = x,
          foc_2 = foc[1]
        )
      )
    }
  ) %>%
  dplyr::bind_rows()

g %>%
  ggplot(
    aes(
      x = x,
      y = foc_2
    )
  ) +
  geom_line() +
  geom_hline(
  yintercept = 0,
  linetype = "dashed"
  ) +
  theme_classic()
```

```{r, results = "asis"}
# without ths = 1
i <- 2
owner <- equilibrium$exogenous[[t]]$owner
index <- owner[i, ] %>% as.logical()
num <- sum(index)
g <-
  seq(
    -10,
    10,
    by = 0.1
  ) %>%
  purrr::map(
    function(x) {
      w_x <- equilibrium$endogenous[[t]]$w
      w_x[2] <- x
      profit <-
        solve_profit_ths_t(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          gamma_w = equilibrium$parameter$gamma_w,
          gamma_f = equilibrium$parameter$gamma_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a = equilibrium$exogenous[[t]]$x_a[index, , drop = FALSE],
          x_c = equilibrium$exogenous[[t]]$x_c[index, , drop = FALSE],
          size_w = equilibrium$exogenous[[t]]$size_w,
          size_f = equilibrium$exogenous[[t]]$size_f,
          owner = equilibrium$exogenous[[t]]$owner[i, index, drop = FALSE],
          mu = equilibrium$shock[[t]]$mu[index, , drop = FALSE],
          ea_w = equilibrium$shock[[t]]$ea_w[index, , drop = FALSE],
          ea_f = equilibrium$shock[[t]]$ea_f[index, , drop = FALSE],
          ec_w = equilibrium$shock[[t]]$ec_w[index, , drop = FALSE],
          ec_f = equilibrium$shock[[t]]$ec_f[index, , drop = FALSE],
          w = w_x[index, , drop = FALSE],
          f = equilibrium$endogenous[[t]]$f[index, , drop = FALSE],
          s_f = equilibrium$endogenous[[t]]$s_f[index, , drop = FALSE],
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      return(
        tibble::tibble(
          x = x,
          profit_2 = profit
        )
      )
    }
  ) %>%
  dplyr::bind_rows()

g %>%
  ggplot(
    aes(
      x = x,
      y = profit_2
    )
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  theme_classic()
```

```{r}
g <-
  seq(
    -10,
    30,
    by = 0.1
  ) %>%
  purrr::map(
    function(x) {
      f_x <- equilibrium$endogenous[[t]]$f
      f_x[2] <- x
      profit <-
        solve_profit_ths_t(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          gamma_w = equilibrium$parameter$gamma_w,
          gamma_f = equilibrium$parameter$gamma_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a = equilibrium$exogenous[[t]]$x_a,
          x_c = equilibrium$exogenous[[t]]$x_c,
          size_w = equilibrium$exogenous[[t]]$size_w,
          size_f = equilibrium$exogenous[[t]]$size_f,
          owner = equilibrium$exogenous[[t]]$owner,
          mu = equilibrium$shock[[t]]$mu,
          ea_w = equilibrium$shock[[t]]$ea_w,
          ea_f = equilibrium$shock[[t]]$ea_f,
          ec_w = equilibrium$shock[[t]]$ec_w,
          ec_f = equilibrium$shock[[t]]$ec_f,
          w = equilibrium$endogenous[[t]]$w,
          f = f_x,
          s_f = equilibrium$endogenous[[t]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      return(
        tibble::tibble(
          x = x,
          profit_2 = profit[2]
        )
      )
    }
  ) %>%
  dplyr::bind_rows()

g %>%
  ggplot(
    aes(
      x = x,
      y = profit_2
    )
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  theme_classic()
```

```{r, results = "asis"}
# with ths = 1
g <-
  seq(
    -10,
    20,
    by = 0.1
  ) %>%
  purrr::map(
    function(x) {
      w_x <- equilibrium$endogenous[[t]]$w
      w_x[2] <- x
      profit <-
        solve_profit_ths_t(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          gamma_w = equilibrium$parameter$gamma_w,
          gamma_f = equilibrium$parameter$gamma_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a = equilibrium$exogenous[[t]]$x_a,
          x_c = equilibrium$exogenous[[t]]$x_c,
          size_w = equilibrium$exogenous[[t]]$size_w,
          size_f = equilibrium$exogenous[[t]]$size_f,
          owner = equilibrium$exogenous[[t]]$owner,
          mu = equilibrium$shock[[t]]$mu,
          ea_w = equilibrium$shock[[t]]$ea_w,
          ea_f = equilibrium$shock[[t]]$ea_f,
          ec_w = equilibrium$shock[[t]]$ec_w,
          ec_f = equilibrium$shock[[t]]$ec_f,
          w = w_x,
          f = equilibrium$endogenous[[t]]$f,
          s_f = equilibrium$endogenous[[t]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      return(
        tibble::tibble(
          x = x,
          profit_2 = profit[2]
        )
      )
    }
  ) %>%
  dplyr::bind_rows()

g %>%
  ggplot(
    aes(
      x = x,
      y = profit_2
    )
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  theme_classic()
```

```{r}
g <-
  seq(
    -10,
    2,
    by = 0.1
  ) %>%
  purrr::map(
    function(x) {
      f_x <- equilibrium$endogenous[[t]]$w
      f_x[2] <- x
      profit <-
        solve_profit_ths_t(
          m_w = equilibrium$parameter$m_w,
          m_f = equilibrium$parameter$m_f,
          beta_w = equilibrium$parameter$beta_w,
          beta_f = equilibrium$parameter$beta_f,
          gamma_w = equilibrium$parameter$gamma_w,
          gamma_f = equilibrium$parameter$gamma_f,
          lambda_w = equilibrium$parameter$lambda_w,
          lambda_f = equilibrium$parameter$lambda_f,
          x_a = equilibrium$exogenous[[t]]$x_a,
          x_c = equilibrium$exogenous[[t]]$x_c,
          size_w = equilibrium$exogenous[[t]]$size_w,
          size_f = equilibrium$exogenous[[t]]$size_f,
          owner = equilibrium$exogenous[[t]]$owner,
          mu = equilibrium$shock[[t]]$mu,
          ea_w = equilibrium$shock[[t]]$ea_w,
          ea_f = equilibrium$shock[[t]]$ea_f,
          ec_w = equilibrium$shock[[t]]$ec_w,
          ec_f = equilibrium$shock[[t]]$ec_f,
          w = equilibrium$endogenous[[t]]$f,
          f = f_x,
          s_f = equilibrium$endogenous[[t]]$s_f,
          method_s_w = equilibrium$constant$method_s_w,
          margin = equilibrium$constant$margin,
          quadrature_size = equilibrium$constant$quadrature_size,
          tol = equilibrium$constant$tol
        ) 
      return(
        tibble::tibble(
          x = x,
          profit_2 = profit[2]
        )
      )
    }
  ) %>%
  dplyr::bind_rows()

g %>%
  ggplot(
    aes(
      x = x,
      y = profit_2
    )
  ) +
  geom_line() +
  geom_hline(
    yintercept = 0,
    linetype = "dashed"
  ) +
  theme_classic()
```

```{r, results = "asis"}
baseline <- 
  evaluate_equilibrium_t(
    x = equilibrium$parameter$m_w,
    target = "m_w",
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
baseline %>%
  kbl() %>%
  kable_styling()
```

## Parameter {.tabset}

### m_w (Matching coefficient of worker) {.tabset}

```{r}
target <- "m_w"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}

compute_elasticity_comparative <- 
  function(
    comparative
    ) {
    df <- comparative %>%
      dplyr::arrange(i) %>%
      dplyr::group_by(i) %>%
      dplyr::mutate(
        percentage_change_w = (w - dplyr::lag(w)) / dplyr::lag(w) * 100,
        percentage_change_f = (f - dplyr::lag(f)) / dplyr::lag(f) * 100,
        percentage_change_s_w = (s_w - dplyr::lag(s_w)) / dplyr::lag(s_w) * 100,
        percentage_change_s_f = (s_f - dplyr::lag(s_f)) / dplyr::lag(s_f) * 100,
        percentage_change_target = (target - dplyr::lag(target)) / dplyr::lag(target) * 100,
        unit_change_target = target - dplyr::lag(target),
        elasticity_w = percentage_change_w / percentage_change_target,
        elasticity_f = percentage_change_f / percentage_change_target,    
        elasticity_s_w = percentage_change_s_w / percentage_change_target,    
        elasticity_s_f = percentage_change_s_f / percentage_change_target,
        semi_elasticity_w = percentage_change_w / unit_change_target,
        semi_elasticity_f = percentage_change_w / unit_change_target, 
        semi_elasticity_s_w = percentage_change_s_w / unit_change_target,    
        semi_elasticity_s_f = percentage_change_s_f / unit_change_target
      ) %>%
      dplyr::ungroup() 
    
    df$target <- target
    
    result_df <- 
      df %>%
      dplyr::select(
        target,
        i,
        elasticity_w,
        elasticity_f,
        elasticity_s_w,
        elasticity_s_f,
        semi_elasticity_w,
        semi_elasticity_f,
        semi_elasticity_s_w,
        semi_elasticity_s_f
      ) 
    
  return(result_df)
  }

compute_elasticity_index <- 
  function(
    comparative
  ){
    base <-
      comparative %>%
      dplyr::pull(target)
    
    base <- base[length(base)/2]
    
    index <- 
      which(
        comparative$target == base
      ) + 1
    
    return(index)
  }

df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )
    
df_old <- 
  df[
  index,
  1:ncol(df)
  ]

```

### beta_w (Worker's utility) {.tabset}

```{r}
target <- "beta_w"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### beta_f (Client firm's utility) {.tabset}

```{r}
target <- "beta_f"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### gamma_w (Cost for handling workers) {.tabset}

```{r}
target <- "gamma_w"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### gamma_f (Cost for handling client firms) {.tabset}

```{r}
target <- "gamma_f"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results = "asis"}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### lambda_w (Wage coefficient) {.tabset}

```{r}
target <- "lambda_w"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### lambda_f (fee coefficient) {.tabset}

```{r}
target <- "lambda_f"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### mu (Matching efficiency of THS) {.tabset}

```{r}
target <- "mu"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### size_w (number of workers) {.tabset}

```{r}
target <- "size_w"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

### size_f (number of firms) {.tabset}

```{r}
target <- "size_f"
comparative <- 
  evaluate_comparative_t(
    target = target,
    t = t,
    equilibrium = equilibrium,
    solver = solver,
    multistart = multistart
  )
```

#### table

```{r, results = "asis"}
comparative %>%
  dplyr::arrange(
    i,
    target
  ) %>%
  kbl() %>%
  kable_styling()
```

```{r, results = "asis"}
p <- 
  plot_comparative(
    comparative = comparative
  )
```

```{r, results='hide'}
df <- 
  compute_elasticity_comparative(
    comparative = comparative
  )

index <- 
  compute_elasticity_index(
    comparative = comparative
  )

df_new <- 
  df[
    index,
    1:ncol(df)
    ]

df_old <- 
  rbind(
    df_old, 
    df_new
    )
```

## Summary table {.tabset}

```{r, results ='asis'}
df_old %>%
  kbl() %>%
  kable_styling()
```
